Time stability in human interaction networks

### 2015-06-19 paper.tex
pequena arrumacao no texto sobre datas

This is a way to enhance the reliability of the methods,
of algorithmic routines, of data consistency,
and of the results themselves.
Also, we believe that this practice raises the scientific contribution of the work,
handing not only the framework and the results, 
but the exact data and processes that render them~\cite{openSci}.

\section{Results and discussion}\label{sec:results}
%Remarkable features from the analysis of the four email lists are:
%\begin{itemize}
%    \item The activity along time is practically the same for all lists, thus suggesting stable patterns.
%    \item The fraction of participants in each Erd\"os sector is stable along time and can be determined even with very few messages 
%    \item The topological metrics combine into principal components in PCA in the same way for all lists and all snapshots (). 
%        \item Symmetry measures of the topology, as defined in this article, present more dispersion than the usual clustering coefficient (Section~\ref{prevalence}).
%    \item Typology speculations are immediate from results (Section~\ref{sec:pty}).
%\end{itemize}
\subsection{Activity along time}\label{constDisc}
The activity along time, in terms of seconds, minutes, hours, days and months,  is practically the same for all lists.
Histograms in each time scale were calculated as were circular average values and their dispersion.
We chose to give detailed values in Table~\ref{tab:circ}-\ref{tab:min2} because these numbers can actually be used for characterizing nodes (participants) in other networks, and networks themselves, as they are independent of the network under analysis. For example, they may serve for identification of outliers in a community.

>>>>

This is a way to enhance the reliability of the methods,
of algorithmic routines, of data consistency,
and of the results themselves.
Also,
by handing not only the framework and the results,
but the exact data and processes that render them,
 this raises the scientific contribution of the work~\cite{openSci}.

%This is a way to enhance the reliability of the methods,
%of algorithmic routines, of data consistency,
%and of the results themselves.
%Also, we believe that this practice raises the scientific contribution of the work,
%handing not only the framework and the results, 
%but the exact data and processes that render them~\cite{openSci}.
\section{Results and discussion}\label{sec:results}
%Remarkable features from the analysis of the four email lists are:
%\begin{itemize}
%    \item The activity along time is practically the same for all lists, thus suggesting stable patterns.
%    \item The fraction of participants in each Erd\"os sector is stable along time and can be determined even with very few messages 
%    \item The topological metrics combine into principal components in PCA in the same way for all lists and all snapshots (). 
%        \item Symmetry measures of the topology, as defined in this article, present more dispersion than the usual clustering coefficient (Section~\ref{prevalence}).
%    \item Typology speculations are immediate from results (Section~\ref{sec:pty}).
%\end{itemize}
\subsection{Activity along time}\label{constDisc}
The activity along time, in terms of seconds, minutes, hours, days and months,  is practically the same for all lists.
Histograms in each time scale were calculated as were circular average values and their dispersion.
We chose to give detailed values in Table~\ref{tab:circ}-\ref{tab:min2} because these numbers can actually be used for characterizing nodes (participants) in other networks, and networks themselves, as they are independent of the network under analysis. For example, they may serve for identification of outliers in a community.
